---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wrapped

This package contains source code for reading your Music (as in, the Apple Music app) listening data into a tidy data frame. I used the output as a starting point for a Wrapped-like analysis of what I listen to. :)

## Installation

You can install wrapped from [GitHub](https://github.com/simonpcouch/wrapped) with:

``` r
# install.packages("devtools")
devtools::install_github("simonpcouch/wrapped")
```

## Usage

The package contains one function, `wrap_library()`, which takes a path to an `.xml` file and a year, and outputs a tidy data frame. 

``` r
wrap_library("Library.xml", 2022L)
```

The `.xml` file should be the output of navigating to:

```
Music > File > Library > Export Library
```

It also contains a data frame, `wrapped`, which is the (slightly modified) output of running this function on my own library:

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tibble)
```

```{r}
library(wrapped)

wrapped
```
